---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

Load in required libraries first.

```{r}
require(ggplot2)
require(data.table)
```

## Loading and preprocessing the data

Let's unpack the data first. (The data is in a zip file in ddthe github repo.)
Unzip and then read in, and do a quick summary.

```{r}
unzip('activity.zip')
z <- read.csv('activity.csv', stringsAsFactors = FALSE)
summary(z)
```

We have some NA's. We just want to ignore those days with missing data.

Let's also aggregate the number of steps by day, and by interval.

```{r}
z1 <- data.table(na.omit(z))
dd1 <- z1[,sum(steps), by = date]
setnames(dd1, 'V1', 'steps')

i <- (z1$interval %/% 100)*12 + (z1$interval %% 100) %/% 5
z1[,'i'] <- i
dd2 <- z1[,mean(steps), by = i]
setnames(dd2, 'V1', 'steps')
setnames(dd2, 'i', 'interval')
str(dd2)

```      

## What is mean total number of steps taken per day?

```{r}
hist(dd1$steps)
m1 <- mean(dd1$steps)
m2 <- median(dd1$steps)
```
So the mean = `r m1`

And the median is `r m2`


## What is the average daily activity pattern?

```{r}
plot(dd2$interval, dd2$steps, type = 'l')
q <- 5* (which(dd2$steps == max(dd2$steps)) - 1)
iv <- (q %/% 60)*100 + (q %% 60)

```

The interval with the greatest average number of steps = `r iv`.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
